A quantitative framework for investigating the reliability of network construction

### 2018-02-14 manuscript/CI_interactions.tex
probably replicated changes to addresses
new priors based on a couple of sample subwebs

\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3,4}$, Kate Wootton$^{3}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip$^2$ Département de biologie\\ 
Université de Sherbrooke\\ 
Sherbrooke, Canada\\ 
\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip $^4$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdispr from the package MASS~\citep{MASS}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.

>>>>

\author{Alyssa R. Cirtwill$^{1}$, Dominique Gravel$^{2}$, \&  Anna Ekl\"{o}f$^{1}$, Tomas Roslin$^{3,4}$, Kate Wootton$^{3}$}
\date{\small$^1$Department of Physics, Chemistry\\ 
and Biology (IFM)\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip$^2$ D\'{e}partement de biologie\\ 
Universit\'{e} de Sherbrooke\\ 
Sherbrooke, Canada\\ 
\medskip $^3$ Department of Ecology\\ P.O. Box 7044, Swedish University of Agricultural Sciences \\ SE-750 07 Uppsala, Sweden \\
\medskip $^4$ Spatial Foodweb Ecology Group\\ Department of Agricultural Sciences \\ PO Box 27 (Latokartanonkaari 5)\\ FI-00014 University of Helsinki, Finland \\
% \medskip
% $^\dagger$ Corresponding author:\\
% alyssa.cirtwill@gmail.com\\
% +46 723 158464\\
}

@@

  First, we must obtain the $\alpha$ and $\beta$ parameters for the prior distribution. In this study we obtained these parameters using the R~\citep{R} function fitdist from the package fitdistrplus~\citep{fitdistrplus}. Once $\alpha$ and $\beta$ are known, we can update them using our observed data. Specifically, we are interested in $\alpha'=\alpha+k$ and $\beta'=\beta+n-k$. These parameters can then be used to calculate a credible interval using the R~\citep{R} function qbeta. In the table below, we present the 95\% credible intervals for \emph{Salix}-galler and galler-natural enemy paris with different numbers of observed co-occurrences ($n$) and no observed interactions ($k=0$). Both sets of intervals rely on prior information from the network in~\citet{Barbour2016,Barbour2016Dryad}.
